\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Mathematical Foundations of the Roguescroll Engine}
\author{Dailiance Team}
\date{\today}

\begin{document}
\maketitle

\section{Core Transformations}

\subsection{Scene Graph Transform}
The scene graph transformation matrix $T$ for a node $n$ is defined as:
\begin{equation}
T_n = \prod_{i=1}^{k} T_{parent_i}
\end{equation}
where $k$ is the depth of the node in the hierarchy.

\subsection{Quaternion Rotation}
For a rotation quaternion $q = (w, x, y, z)$, the rotation matrix $R$ is:
\begin{equation}
R = \begin{bmatrix}
1-2y^2-2z^2 & 2xy-2wz & 2xz+2wy \\
2xy+2wz & 1-2x^2-2z^2 & 2yz-2wx \\
2xz-2wy & 2yz+2wx & 1-2x^2-2y^2
\end{bmatrix}
\end{equation}

\section{Physics System}

\subsection{Rigidbody Dynamics}
The equations of motion for a rigidbody:
\begin{equation}
\begin{aligned}
F &= m\ddot{x} \\
\tau &= I\dot{\omega} + \omega \times (I\omega)
\end{aligned}
\end{equation}
where $F$ is force, $m$ is mass, $\tau$ is torque, $I$ is inertia tensor, and $\omega$ is angular velocity.

\subsection{Collision Response}
For a collision between bodies $A$ and $B$:
\begin{equation}
\begin{aligned}
v'_A &= v_A - \frac{(1+e)(v_A - v_B) \cdot n}{1/m_A + 1/m_B} \frac{n}{m_A} \\
v'_B &= v_B + \frac{(1+e)(v_A - v_B) \cdot n}{1/m_A + 1/m_B} \frac{n}{m_B}
\end{aligned}
\end{equation}
where $e$ is the coefficient of restitution and $n$ is the collision normal.

\section{Network System}

\subsection{P2P Connection Graph}
For a network of $n$ peers, the connection matrix $C$ is:
\begin{equation}
C_{ij} = \begin{cases}
1 & \text{if peer } i \text{ is connected to peer } j \\
0 & \text{otherwise}
\end{cases}
\end{equation}

\subsection{Message Propagation}
The probability of message delivery $P$ through $k$ hops:
\begin{equation}
P(k) = \prod_{i=1}^{k} p_i
\end{equation}
where $p_i$ is the reliability of each hop.

\section{Actor System}

\subsection{State Transition}
For an actor $A$ with state $s$:
\begin{equation}
s_{t+1} = f(s_t, a_t, \omega_t)
\end{equation}
where $a_t$ is the action and $\omega_t$ is the environment state.

\subsection{Ownership Verification}
The ownership proof $\pi$ for an actor $A$:
\begin{equation}
\pi = H(H(A) || H(owner) || timestamp)
\end{equation}
where $H$ is a cryptographic hash function.

\section{Rendering System}

\subsection{View Frustum}
The view frustum planes are defined by:
\begin{equation}
\begin{aligned}
\text{Near}: & \quad n \cdot p + d_n = 0 \\
\text{Far}: & \quad f \cdot p + d_f = 0 \\
\text{Left}: & \quad l \cdot p + d_l = 0 \\
\text{Right}: & \quad r \cdot p + d_r = 0 \\
\text{Top}: & \quad t \cdot p + d_t = 0 \\
\text{Bottom}: & \quad b \cdot p + d_b = 0
\end{aligned}
\end{equation}

\subsection{Lighting Model}
The Phong lighting equation:
\begin{equation}
I = k_a i_a + k_d i_d (n \cdot l) + k_s i_s (r \cdot v)^\alpha
\end{equation}
where $k$ are material properties, $i$ are light intensities, and $\alpha$ is the shininess factor.

\section{Anti-DDOS System}

\subsection{Reputation Score}
The reputation $R$ for a client $C$:
\begin{equation}
R(C) = \frac{\sum_{i=1}^{n} w_i s_i}{\sum_{i=1}^{n} w_i}
\end{equation}
where $w_i$ are weights and $s_i$ are individual scores.

\subsection{Connection Rate Limiting}
The allowed connection rate $\lambda$:
\begin{equation}
\lambda = \lambda_{base} \cdot e^{-R(C)}
\end{equation}
where $\lambda_{base}$ is the base rate limit.

\section{ICP Integration}

\subsection{Canister State}
The state $S$ of a canister $C$:
\begin{equation}
S(C) = (H, T, B)
\end{equation}
where $H$ is the hash of the current state, $T$ is the timestamp, and $B$ is the balance.

\subsection{Consensus Verification}
The consensus proof $\Pi$:
\begin{equation}
\Pi = \prod_{i=1}^{n} H(S_i)
\end{equation}
where $S_i$ are the states of participating nodes.

\end{document} 